---
title: "From Manuscript to R Package"
author: "Maya Gans"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    seal: false
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      titleSlideClass: ["bottom", "left"]
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: "16:9"
      countIncrementalSlides: true
---

class: right middle hide-count
background-color: white
background-position: left

<link href="https://fonts.googleapis.com/css?family=Cedarville+Cursive|Karla|Montserrat|Open+Sans|Quattrocento|Raleway&display=swap" rel="stylesheet">


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(highlight = TRUE, warning = FALSE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
mono_light(
  white_color = "#fff",
  header_font_google = google_font("Cedarville Cursive", "600"),
  text_font_google = google_font("Karla", "300", "300i"),
  code_font_google = google_font("Fira Code"),
  text_font_size = "24px",
  code_font_size = "1.2em"
)

opaque_box <- function(x) {
  htmltools::tags$div(
    class = "f1 bg-white-o90 pa6 shadow-3 h-75",
    htmltools::tags$h1(htmltools::tags$em(x))
  )
}

```

```{r xaringan-animate-all, echo=FALSE}
xaringanExtra::use_animate_all("fade")
xaringanExtra::use_tachyons()
xaringanExtra::use_text_poster()
```

```{css echo=FALSE}
a, a > code {
  color: #D55E00FF;
  text-decoration: none;
}

em {
  color: #D55E00FF;
  font-style: normal;
}

del {
  color: #E5E5E5;
  text-decoration: none;
  font-weight: normal;
}

.inverse del {
  color: #6C7B7F;
}

.bg-white-o90{
   background-color: rgba(255, 255, 255, 0.9);
}

.large { font-size: 175% }

.hide-count .remark-slide-number {
  display: none;
}

.text-poster {
	font-family: 'Cinzel', serif;
}

.inverse {
  color: #b9bfca;
  background-color: #282D35
}

.inverse.remark-slide-number {
  color: #b9bfca;
}

.remark-code-line-highlighted {
  color: #D55E00FF;
  background-color: transparent;
}

.remark-inline-code {
  color: #b9bfca;
}

.smaller-code {
  font-size: 20px;
}

.h2 {
  font-family: 'Karla'
}

div.overview {
  font-family: 'Cedarville Cursive';
  color: white;
  background-color: #D55E00FF;
  font-size: 2rem;
}
```

.pull-right[
  # From Manuscript to R Package
]

Maya Gans

`r fontawesome::fa("twitter", fill = "#282D35")` @mayacelium

Slides: [bit.ly/manuscriptrpackage](http://bit.ly/manuscriptrpackage)

---

# You Already

- structure your project
- write R code 
- declare dependencies
- test your code
- document your code
- clean your data
- write reports
- share your code

<div style="text-align:right;color:#D55E00FF;font-family:'Cedarville Cursive';font-size:2em;position:absolute;bottom:100px;right:100px;">
So let's do it as a package!
</div>
---

class: center, middle, hide-count
background-size: cover

.overview[
`r opaque_box("You already<br>structure your project")`
]

---

class: inverse, large

```
├── data/
├── reports/
├── scripts/
└── analysis.Rproj
```

---

class: inverse, large

```
├── data/
├── reports/
*├── R/
└── analysis.Rproj
```

---

class: inverse, large

```
*├── data/
├── reports/
├── R/
└── analysis.Rproj
```

---

class: inverse, large

```
├── data/ 
*├── vignettes/
├── R/
└── analysis.Rproj
```

---

class: inverse, large

```
├── data/ 
├── vignettes/ 
├── R/
*├── man/
*├── tests/
*├── DESCRIPTION
*├── NAMESPACE
└── analysis.Rproj
```

---

class: inverse, large

```
├── data/ 
├── vignettes/ 
├── R/
├── man/ 
├── tests/ 
*├── DESCRIPTION
├── NAMESPACE
└── analysis.Rproj
```

---

class: inverse, large


.smaller-code[
```
Package: manuscriptrpackage
Title: What the Package Does (One Line, Title Case)
Version: 0.0.0.9000
Authors@R: 
    person(given = "Maya",
           family = "Gans",
           role = c("aut", "cre"),
           email = "jaffe.maya@gmail.com")
Description: What the package does (one paragraph).
License: MIT + file LICENSE
Encoding: UTF-8
LazyData: true
```
]

---

class: middle, inverse

```{r, echo=FALSE}
knitr::include_graphics("img/svg/create_project.svg")
```

---

class: center, middle, hide-count

.overview[
`r opaque_box("You already<br>write R code")`
]

---

class: middle, inverse

```{r, echo=FALSE}
knitr::include_graphics("img/svg/write_code.svg")
```

---

class: middle, inverse

```{r, echo=FALSE}
knitr::include_graphics("img/svg/use_r.svg")
```

---

class: middle, inverse

```{r, echo=FALSE}
knitr::include_graphics("img/svg/write_functions.svg")
```

---

class: middle, inverse

```{r, echo=FALSE}
knitr::include_graphics("img/svg/load_all.svg")
```

---


class: center, middle, hide-count

.overview[
`r opaque_box("You already<br>declare your dependencies")`
]

---

class: middle, inverse

```{r, echo=FALSE}
knitr::include_graphics("img/svg/write_library.svg")
```

---

class: middle, inverse

```{r, echo=FALSE}
knitr::include_graphics("img/svg/use_package.svg")
```

---

class: middle, inverse

```{r, echo=FALSE}
knitr::include_graphics("img/svg/use_package_code.svg")
```

---

class: inverse, large

.smaller-code[
```
Package: manuscriptrpackage
Title: What the Package Does (One Line, Title Case)
Version: 0.0.0.9000
Authors@R: 
    person(given = "Maya",
           family = "Gans",
           role = c("aut", "cre"),
           email = "jaffe.maya@gmail.com")
Description: What the package does (one paragraph).
License: MIT + file LICENSE
Encoding: UTF-8
LazyData: true
```
]

---

class: inverse, large

.smaller-code[
```
Package: manuscriptrpackage
Title: What the Package Does (One Line, Title Case)
Version: 0.0.0.9000
Authors@R: 
    person(given = "Maya",
           family = "Gans",
           role = c("aut", "cre"),
           email = "jaffe.maya@gmail.com")
Description: What the package does (one paragraph).
License: MIT + file LICENSE
Encoding: UTF-8
LazyData: true
*Imports: 
*    ggplot2
*    dplyr
```
]

---

class: middle, inverse

```{r, echo=FALSE}
knitr::include_graphics("img/svg/use_package_install.svg")
```

---

class: center, middle, hide-count


.overview[
`r opaque_box("You already<br>test your code")`
]

---

class: middle, inverse

```{r, echo=FALSE}
knitr::include_graphics("img/svg/fiddle.svg")
```

---

class: middle, inverse

```{r, echo=FALSE}
knitr::include_graphics("img/svg/use_test.svg")
```

---

class: center, middle, hide-count

.overview[
`r opaque_box("You already<br>document your code")`
]

---

class: middle, inverse

```{r, echo=FALSE}
knitr::include_graphics("img/svg/comment.svg")
```

---

class: middle, inverse

```{r, echo=FALSE}
knitr::include_graphics("img/svg/use_roxygen_rmd.svg")
```

---

class: middle, inverse

```
#' Plot mean sepal length by species
#'
#' @param size the size of the points
#'
#' @return a ggplot
#' @export
#'
#' @examples
#'
#' plot_iris()
#'
plot_iris <- function(size = 2) {
  iris %>%
    dplyr::group_by(Species) %>%
    dplyr::summarize(mean_sepal_length = mean(Sepal.Length)) %>%
    ggplot2::ggplot(ggplot2::aes(mean_sepal_length, Species)) +
    ggplot2::geom_point(size = 2)
}
```

---

class: middle, inverse

```{r, echo=FALSE}
knitr::include_graphics("img/svg/document.svg")
```

---

class: center, middle, hide-count

.overview[
`r opaque_box("You already<br>clean your data")`
]

---

class: middle, inverse

```{r, echo=FALSE}
knitr::include_graphics("img/svg/use_data_raw.svg")
```

---

class: middle, inverse

```{r, echo=FALSE}
knitr::include_graphics("img/svg/use_data.svg")
```

---

class: center, middle, hide-count

.overview[
`r opaque_box("You already<br>write reports")`
]

---

class: middle, inverse

```{r, echo=FALSE}
knitr::include_graphics("img/svg/use_vignette.svg")
```


---

class: middle, inverse

```{r, echo=FALSE}
knitr::include_graphics("img/svg/use_inst.svg")
```

---

class: middle, inverse

```{r, echo=FALSE}
knitr::include_graphics("img/svg/use_toplevel.svg")
```

---

class: center, middle, hide-count

.overview[
`r opaque_box("You already<br>share your code")`
]

---

class: middle, inverse

```{r, echo=FALSE}
knitr::include_graphics("img/svg/install.svg")
```

---

class: center, middle, hide-count

.overview[
`r opaque_box("Thank you!!")`
]

---
